Pigeons.jl: Distributed sampling from intractable distributions

### 2023-10-30 paper.tex
Revert "Remove inputs and place in main tex"
This reverts commit 5fa4b448d674f0740c463b4df871991756a7c766.

\section{Acknowledgements}
NS acknowledges the support of a Vanier Canada Graduate Scholarship. 
PT acknowledges the support of the Black Hole Initiative at Harvard University, 
which is funded by grants from the John Templeton Foundation and the 
Gordon and Betty Moore Foundation to Harvard University, 
as well as support by the National Science Foundation grants AST-1935980 
and AST-2034306 and the Gordon and Betty Moore Foundation (GBMF-10423).
SS acknowledges the support of EPSRC grant EP/R034710/1 CoSines.
ABC and TC acknowledge the support of an NSERC Discovery Grant.
We also acknowledge use of the ARC Sockeye computing platform from the
University of British Columbia, as well as cloud computing resources provided 
by Oracle.

>>>>

\section{Acknowledgements}
NS acknowledges the support of a Vanier Canada Graduate Scholarship. 
PT acknowledges the support of the Black Hole Initiative at Harvard University, 
which is funded by grants from the John Templeton Foundation and the 
Gordon and Betty Moore Foundation to Harvard University.
PT also acknowledges support by the National Science Foundation grants AST-1935980 
and AST-2034306 and the Gordon and Betty Moore Foundation (GBMF-10423).
SS acknowledges the support of EPSRC grant EP/R034710/1 CoSines.
ABC and TC acknowledge the support of an NSERC Discovery Grant.
We also acknowledge use of the ARC Sockeye computing platform from the
University of British Columbia, as well as cloud computing resources provided 
by Oracle.
